---
title: "week4"
knitr:
  opts_chunk: 
    fig.path: Images/
number-sections: true
number-depth: 3
theme: minty
format:
  memo-pdf:
    default
  report-pdf:
   toc: true
   toc_depth: 2
   number_sections: true
   highlight: tango
header-includes:
  - \usepackage{xcolor}
  - \usepackage{sectsty}
  - \sectionfont{\color{olive}}
---

```{css}
figcaption {
  text-align: center;
}
```
Here are some more changes

Some more changes!

## Executive Summary

## Introduction {#sec-introduction}

```{r}
#| echo: false
#| warning: false
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE
)

df <- randu
```

```{r}
#| echo: true
library(tidyverse)
library(palmerpenguins)
```

### Subsection 1.1 {#sec-subsection}

Here is some text

```{r}
#| label: fig-penguins-plot
#| fig-cap: "Penguin bill length and bill depth, coloured by species"
ggplot(penguins, aes(x=bill_length_mm, y=bill_depth_mm, colour = species)) +
  geom_point()
```

```{r}
#| label: fig-penguins-flipper
#| fig-cap: "Penguin bill length and flipper length, coloured by species"
#| lst-label: lst-penguins-code
#| lst-cap: "Code to produce penguins plot"
ggplot(penguins, aes(x=bill_length_mm, y=flipper_length_mm, colour = species)) +
  geom_point()

df <- randu
```

Cross reference to @lst-penguins-code

## A whole new section

Remember in the @sec-introduction, @fig-penguins-flipper showed us the flipper length as opposed to @fig-penguins-plot. Test for @sec-subsection

```{r}
#| label: tbl-summarytable

knitr::kable(head(penguins), caption = "Summary of the penguins dataset")
```

@tbl-summarytable shows us a summary of `penguins`.
